---
title: "TAV-EVT analysis for JCAL"
output: 
  html_document:
    toc: true
    toc_float: true
date: "2020-02-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,warning=FALSE)
```

# Loading, setting up

```{r}
library(readxl)
library(tidyverse)
library(lavaan)
library(semTools)
library(jmRtools) # devtools::install_github("jrosen48/jmRtools")

d <- read_excel("R_Dataset_v2.xlsx")
```

```{r}
# - expctncy_s__23 (Needs to be reversed)
d$expectancy_success__23 <- sjmisc::rec(d$expectancy_success__23, rec = "1=5;2=4;3=3;4=2;5=1")
```

# Preliminary analysis

## Checking for missing data

no missingness in this data

```{r}
# d %>% select(tam_perceived_usefulness_1:full_cost_emotional_cost_59) %>% complete.cases()
d %>% select(tam_perceived_usefulness_1:full_cost_emotional_cost_59) %>% complete.cases() %>% table()
```

## Demographic info

```{r}
# age
d %>% 
  skimr::skim(Q3)

# gender
d %>% 
  janitor::tabyl(Q29)

# ethnic background
d %>% 
  janitor::tabyl(Q31) %>% arrange(desc(n)) %>% data.table::data.table()

# english first language
d %>% 
  janitor::tabyl(Q26)

# computer access at home, years of usage, hours of use not examined
```

## Descriptives at the item-level

```{r}
d %>% select(tam_perceived_usefulness_1:full_cost_emotional_cost_59) %>% 
  mutate_all(as.numeric) %>% 
  psych::describe()
```

```{r}
d %>% 
  select(tam_perceived_usefulness_1:full_cost_emotional_cost_59) %>% 
  mutate_all(as.numeric) %>% 
  corrr::correlate()
```

## Descriptives at the composite level 

```{r}

composite_mean_maker <- function (x, ...) {
  out <- dplyr::select(x, ...)
  out <- mutate_all(out, as.numeric)
  out <- apply(out, 1, function(x) mean(x, na.rm = T))
  out[is.nan(out)] <- NA
  return(out)
}

o <- d %>% 
  transmute(perceived_usefulness = composite_mean_maker(., tam_perceived_usefulness_1,
                                                        tam_perceived_usefulness_9,
                                                        tam_perceived_usefulness_11,
                                                        tam_perceived_usefulness_15),
            subjective_norms = composite_mean_maker(., 
                                                    tam_subjective_norm_2,
                                                    tam_subjective_norm_4),
            facilitating_conditions = composite_mean_maker(.,
                                                          tam_facilitating_condition_5,
                                                          tam_facilitating_condition_13),
            perceived_ease_use = composite_mean_maker(., tam_perceived_ease_use_3,
                                                      tam_perceived_ease_use_10,
                                                      # tam_perceived_ease_use_12,
                                                      tam_perceived_ease_use_16),
            computer_attitudes = composite_mean_maker(., tam_computer_attitudes_6,
                                                      tam_computer_attitudes_7,
                                                      tam_computer_attitudes_8,
                                                      tam_computer_attitudes_14),
            #tam_computer_attitudes_17),
            attainment = composite_mean_maker(., task_value_attainment_value_27,
                                              task_value_attainment_value_31,
                                              task_value_attainment_value_33,
                                              task_value_attainment_value_36,
                                              task_value_attainment_value_38),
            interest = composite_mean_maker(., task_value_interest_value_29,
                                            task_value_interest_value_32,
                                            task_value_interest_value_37,
                                            task_value_interest_value_40),
            utility = composite_mean_maker(., task_value_utility_value_28,
                                           task_value_utility_value_30,
                                           task_value_utility_value_34,
                                           task_value_utility_value_35,
                                           task_value_utility_value_39),
            expectancy = composite_mean_maker(., expectancy_success__20,
                                              expectancy_success__21,
                                              expectancy_success__22,
                                              #expectancy_success__23,
                                              expectancy_success__24,
                                              expectancy_success__25),
            task_value = composite_mean_maker(., task_value_attainment_value_27,
                                              task_value_attainment_value_31, 
                                              task_value_attainment_value_33,
                                              task_value_attainment_value_36,
                                              task_value_attainment_value_38,
                                              task_value_interest_value_29,
                                              task_value_interest_value_32,
                                              task_value_interest_value_37,
                                              task_value_interest_value_40,
                                              task_value_utility_value_28,
                                              task_value_utility_value_30,
                                              task_value_utility_value_34,
                                              task_value_utility_value_35,
                                              task_value_utility_value_39),
            task_effort = composite_mean_maker(., full_cost_task_effort_cost_42,
                                               full_cost_task_effort_cost_45,
                                               full_cost_task_effort_cost_46,
                                               full_cost_task_effort_cost_51,
                                               full_cost_task_effort_cost_57),
            outside_effort = composite_mean_maker(., full_cost_outside_effort_cost_44,
                                                  full_cost_outside_effort_cost_47,
                                                  full_cost_outside_effort_cost_50,
                                                  full_cost_outside_effort_cost_52),
            lova = composite_mean_maker(., full_cost_loss_valued_alternatives_43,
                                        full_cost_loss_valued_alternatives_49,
                                        full_cost_loss_valued_alternatives_53,
                                        full_cost_loss_valued_alternatives_56),
            emotional_costs = composite_mean_maker(., full_cost_emotional_cost_41,
                                                   full_cost_emotional_cost_48,
                                                   full_cost_emotional_cost_54,
                                                   full_cost_emotional_cost_55,
                                                   full_cost_emotional_cost_58,
                                                   full_cost_emotional_cost_59),
            cost = composite_mean_maker(., full_cost_task_effort_cost_42,
                                        full_cost_task_effort_cost_45,
                                        full_cost_task_effort_cost_46,
                                        full_cost_task_effort_cost_51,
                                        full_cost_task_effort_cost_57,
                                        full_cost_outside_effort_cost_44,
                                        full_cost_outside_effort_cost_47,
                                        full_cost_outside_effort_cost_50,
                                        full_cost_outside_effort_cost_52,
                                        full_cost_loss_valued_alternatives_43,
                                        full_cost_loss_valued_alternatives_49,
                                        full_cost_loss_valued_alternatives_53,
                                        full_cost_loss_valued_alternatives_56,
                                        full_cost_emotional_cost_41,
                                        full_cost_emotional_cost_48,
                                        full_cost_emotional_cost_54,
                                        full_cost_emotional_cost_55,
                                        full_cost_emotional_cost_58,
                                        full_cost_emotional_cost_59),
            behavioral_intentions = composite_mean_maker(., intention_use__18, intention_use__19),
            Site)
```

```{r}
o %>% 
  select(perceived_usefulness,
         perceived_ease_use,
         computer_attitudes,
         behavioral_intentions,
         subjective_norms,
         facilitating_conditions,
         attainment,
         interest,
         utility,
         expectancy,
         task_effort,
         outside_effort,
         lova,
         emotional_costs) %>% 
  psych::describe()
```

```{r}
o %>% 
  select(perceived_usefulness,
         perceived_ease_use,
         computer_attitudes,
         behavioral_intentions,
         subjective_norms,
         facilitating_conditions,
         attainment,
         interest,
         utility,
         expectancy,
         task_effort,
         outside_effort,
         lova,
         emotional_costs) %>% 
  apaTables::apa.cor.table(filename = "composite-descriptives.doc")
```

# Means (and SD) by site

```{r}
o %>% 
  group_by(Site) %>% 
  skimr::skim() %>% 
  DT::datatable()
```

## Manova by site (overall)

```{r}
res.man <- manova(cbind(perceived_usefulness,
                        perceived_ease_use,
                        computer_attitudes,
                        behavioral_intentions,
                        subjective_norms,
                        facilitating_conditions,
                        attainment,
                        interest,
                        utility,
                        expectancy,
                        task_effort,
                        outside_effort,
                        lova,
                        emotional_costs) ~ Site, data = o)

summary(res.man)
# summary.aov(res.man)
```

## Manova by site (by groups of variables)

```{r}
man_tam <- manova(cbind(perceived_usefulness,
                        perceived_ease_use,
                        computer_attitudes,
                        behavioral_intentions,
                        subjective_norms,
                        facilitating_conditions) ~ Site, data = o)

man_evt <- manova(cbind(attainment,
                        interest,
                        utility,
                        expectancy) ~ Site, data = o)

man_cost <- manova(cbind(task_effort,
                         outside_effort,
                         lova,
                         emotional_costs) ~ Site, data = o)

summary(man_tam)
#summary.aov(man_tam)

summary(man_evt)
#summary.aov(man_evt)

summary(man_cost)
#summary.aov(man_cost)
```

# Stage 1

Changes made:
- tm_prcvd_s__12 - tam_perceived_ease_use_12 - done  
- tm_cmptr_tt_17 - tam_computer_attitudes_17 - done  

## A two-factor CFA will be conducted on the subjective norms and facilitating conditions scales (see “independent variables”; Teo et al. (2008).

```{r}
fitmod <- '

# factors 

subjective_norms =~ 
tam_subjective_norm_2 +
tam_subjective_norm_4

facilitating_conditions =~ 
tam_facilitating_condition_5 +
tam_facilitating_condition_13
'

m1 <- cfa(fitmod, data = d)
summary(m1, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
reliability(m1)
# run the code below to confirm that the above gives the same values for alpha
# psych::alpha(data.frame(d$tam_subjective_norm_2, d$tam_subjective_norm_4))
lavInspect(m1)
```

## A separate two-factor CFA will be conducted on perceived usefulness and perceived ease of use (see “mediators”; Teo et al., 2008)

```{r}
fitmod <- '

# factors 

perceived_usefulness =~ 
tam_perceived_usefulness_1 + 
tam_perceived_usefulness_9 + 
tam_perceived_usefulness_11 +
tam_perceived_usefulness_15

perceived_ease_use =~ 
tam_perceived_ease_use_3 + 
tam_perceived_ease_use_10 + 
# tam_perceived_ease_use_12 +
tam_perceived_ease_use_16
'

m2 <- cfa(fitmod, data = d)
summary(m2, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
reliability(m2)
```

## A one-factor CFA will be conducted on the computer attitude scale (see “dependent variables”; Teo et al., 2008)

```{r}
fitmod <- '

# factors 

computer_attitudes =~ 
tam_computer_attitudes_6 +
tam_computer_attitudes_7 +
tam_computer_attitudes_8 +
tam_computer_attitudes_14
# tam_computer_attitudes_17

'

m3 <- cfa(fitmod, data = d)
summary(m3, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
reliability(m3)
```

## First, a four-factor CFA will be conducted on interest value, attainment value, utility value, and expectancy for success

```{r}
fitmod <- '

attainment =~ 
task_value_attainment_value_27 +
task_value_attainment_value_31 +
task_value_attainment_value_33 + 
task_value_attainment_value_36 +
task_value_attainment_value_38

interest =~
task_value_interest_value_29 + 
task_value_interest_value_32 +
task_value_interest_value_37 + 
task_value_interest_value_40

utility =~
task_value_utility_value_28 + 
task_value_utility_value_30 +
task_value_utility_value_34 + 
task_value_utility_value_35 +
task_value_utility_value_39

expectancy =~ 
expectancy_success__20 +
expectancy_success__21 +
expectancy_success__22 +
# expectancy_success__23 +
expectancy_success__24 +
expectancy_success__25

'

m4 <- cfa(fitmod, data = d)
summary(m4, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
reliability(m4)
```

## Since interest value, attainment value, and utility value are often highly correlated (e.g., Linnenbrink-Garcia et al., 2018), a competing CFA will be conducted with expectancy for success and task value (interest, attainment, and utility value).)

```{r}
fitmod <- '

# factors 

task_value =~ 
task_value_attainment_value_27 +
task_value_attainment_value_31 +
task_value_attainment_value_33 + 
task_value_attainment_value_36 +
task_value_attainment_value_38 +
task_value_interest_value_29 + 
task_value_interest_value_32 +
task_value_interest_value_37 + 
task_value_interest_value_40 +
task_value_utility_value_28 + 
task_value_utility_value_30 +
task_value_utility_value_34 + 
task_value_utility_value_35 +
task_value_utility_value_39

expectancy =~ 
expectancy_success__20 +
expectancy_success__21 +
expectancy_success__22 +
# expectancy_success__23 +
expectancy_success__24 +
expectancy_success__25

'

m5 <- cfa(fitmod, data = d)
summary(m5, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
reliability(m5)
```

## A four-factor CFA will be conducted on task effort cost, outside effort cost, loss of valued alternatives, and emotional cost.

```{r}
fitmod <- '

task_effort =~ 
full_cost_task_effort_cost_42 + 
full_cost_task_effort_cost_45 +
full_cost_task_effort_cost_46 + 
full_cost_task_effort_cost_51 +
full_cost_task_effort_cost_57

outside_effort =~
full_cost_outside_effort_cost_44 +
full_cost_outside_effort_cost_47 +
full_cost_outside_effort_cost_50 +
full_cost_outside_effort_cost_52

lova =~ 
full_cost_loss_valued_alternatives_43 +
full_cost_loss_valued_alternatives_49 +
full_cost_loss_valued_alternatives_53 + 
full_cost_loss_valued_alternatives_56

emotional_costs =~
full_cost_emotional_cost_41 + 
full_cost_emotional_cost_48 +
full_cost_emotional_cost_54 + 
full_cost_emotional_cost_55 +
full_cost_emotional_cost_58 + 
full_cost_emotional_cost_59

'

m6 <- cfa(fitmod, data = d)
summary(m6, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
reliability(m6)
```

## Next, since these four cost factors are often highly correlated (see Flake et al., 2015), a one-factor CFA will be conducted for an overall cost factor.

```{r}
fitmod <- '

cost =~ 
full_cost_task_effort_cost_42 + 
full_cost_task_effort_cost_45 +
full_cost_task_effort_cost_46 + 
full_cost_task_effort_cost_51 +
full_cost_task_effort_cost_57 +
full_cost_outside_effort_cost_44 +
full_cost_outside_effort_cost_47 +
full_cost_outside_effort_cost_50 +
full_cost_outside_effort_cost_52 +
full_cost_loss_valued_alternatives_43 +
full_cost_loss_valued_alternatives_49 +
full_cost_loss_valued_alternatives_53 + 
full_cost_loss_valued_alternatives_56 +
full_cost_emotional_cost_41 + 
full_cost_emotional_cost_48 +
full_cost_emotional_cost_54 + 
full_cost_emotional_cost_55 +
full_cost_emotional_cost_58 + 
full_cost_emotional_cost_59

'

m7 <- cfa(fitmod, data = d)
summary(m7, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
reliability(m7)
```

## A final CFA will be conducted as one factor on the behavioral intentions items (Liu et al., 2010; Taylor & Todd, 1995; Venkatesh & Davis, 1996)

```{r}
fitmod <- '

behavioral_intentions =~
intention_use__18 +
intention_use__19

'

m8 <- cfa(fitmod, data = d)
summary(m8, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
reliability(m8)
```

# Stage 2

## The first model (Figure 1) will attempt to replicate the model established in Teo et al. (2008). Specifically, facilitating conditions and subjective norms will predict ease of use and usefulness, ease of use will predict usefulness, and computer attitude will be the final endogenous factor. 

```{r}
fitmod <- '

# factors 

subjective_norms =~ 
tam_subjective_norm_2 +
tam_subjective_norm_4

facilitating_conditions =~ 
tam_facilitating_condition_5 +
tam_facilitating_condition_13

perceived_usefulness =~ 
tam_perceived_usefulness_1 + 
tam_perceived_usefulness_9 + 
tam_perceived_usefulness_11 +
tam_perceived_usefulness_15

perceived_ease_use =~ 
tam_perceived_ease_use_3 + 
tam_perceived_ease_use_10 + 
# tam_perceived_ease_use_12 +
tam_perceived_ease_use_16

computer_attitudes =~ 
tam_computer_attitudes_6 +
tam_computer_attitudes_7 +
tam_computer_attitudes_8 +
tam_computer_attitudes_14
# tam_computer_attitudes_17

# regressions

computer_attitudes ~ perceived_ease_use + perceived_usefulness + subjective_norms + facilitating_conditions
perceived_ease_use ~ facilitating_conditions
perceived_usefulness ~  subjective_norms + perceived_ease_use
'

m2_1 <- sem(fitmod, data = d, meanstructure = T)
summary(m2_1, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
```

## The second model (Figure 2) will extend Teo et al.’s (2008) original model by including behavioral intentions as a final endogenous variable, which will be predicted by computer attitude. 

```{r}
fitmod <- '

# factors 

subjective_norms =~ 
tam_subjective_norm_2 +
tam_subjective_norm_4

facilitating_conditions =~ 
tam_facilitating_condition_5 +
tam_facilitating_condition_13

perceived_usefulness =~ 
tam_perceived_usefulness_1 + 
tam_perceived_usefulness_9 + 
tam_perceived_usefulness_11 +
tam_perceived_usefulness_15

perceived_ease_use =~ 
tam_perceived_ease_use_3 + 
tam_perceived_ease_use_10 + 
# tam_perceived_ease_use_12 +
tam_perceived_ease_use_16

computer_attitudes =~ 
tam_computer_attitudes_6 +
tam_computer_attitudes_7 +
tam_computer_attitudes_8 +
tam_computer_attitudes_14
# tam_computer_attitudes_17

behavioral_intentions =~
intention_use__18 +
intention_use__19

# regressions

computer_attitudes ~ perceived_ease_use + perceived_usefulness + subjective_norms + facilitating_conditions
perceived_ease_use ~ facilitating_conditions
perceived_usefulness ~  subjective_norms + perceived_ease_use
behavioral_intentions ~ computer_attitudes
'

m2_2 <- sem(fitmod, data = d)
summary(m2_2, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
```

# Stage 3

John comment: can you run the "Stage 3" analyses (the third and fourth models) again with expectancy, overall task value, and overall cost

## The third model (Figure 3) is based on the EVT and will examine expectancy, values, and costs as mediators of attitudes and behavioral intentions.

```{r}
fitmod <- '

# factors 

computer_attitudes =~ 
tam_computer_attitudes_6 +
tam_computer_attitudes_7 +
tam_computer_attitudes_8 +
tam_computer_attitudes_14
# tam_computer_attitudes_17

expectancy =~ 
expectancy_success__20 +
expectancy_success__21 +
expectancy_success__22 +
# expectancy_success__23 +
expectancy_success__24 +
expectancy_success__25

attainment =~ 
task_value_attainment_value_27 +
task_value_attainment_value_31 +
task_value_attainment_value_33 + 
task_value_attainment_value_36 +
task_value_attainment_value_38

interest =~
task_value_interest_value_29 + 
task_value_interest_value_32 +
task_value_interest_value_37 + 
task_value_interest_value_40

utility =~
task_value_utility_value_28 + 
task_value_utility_value_30 +
task_value_utility_value_34 + 
task_value_utility_value_35 +
task_value_utility_value_39

task_effort =~ 
full_cost_task_effort_cost_42 + 
full_cost_task_effort_cost_45 +
full_cost_task_effort_cost_46 + 
full_cost_task_effort_cost_51 +
full_cost_task_effort_cost_57

outside_effort =~
full_cost_outside_effort_cost_44 +
full_cost_outside_effort_cost_47 +
full_cost_outside_effort_cost_50 +
full_cost_outside_effort_cost_52

lova =~ 
full_cost_loss_valued_alternatives_43 +
full_cost_loss_valued_alternatives_49 +
full_cost_loss_valued_alternatives_53 + 
full_cost_loss_valued_alternatives_56

emotional_costs =~
full_cost_emotional_cost_41 + 
full_cost_emotional_cost_48 +
full_cost_emotional_cost_54 + 
full_cost_emotional_cost_55 +
full_cost_emotional_cost_58 + 
full_cost_emotional_cost_59

behavioral_intentions =~
intention_use__18 +
intention_use__19

# regressions

expectancy ~ computer_attitudes
attainment ~ computer_attitudes
interest ~ computer_attitudes
utility ~ computer_attitudes
task_effort ~ computer_attitudes
outside_effort ~ computer_attitudes
lova ~ computer_attitudes
emotional_costs ~ computer_attitudes

behavioral_intentions ~ 
expectancy +
attainment +
interest +
utility +
task_effort +
outside_effort +
lova + 
emotional_costs
'

m2_3 <- sem(fitmod, data = d)
summary(m2_3, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
```

## The fourth model (Figure 4) is guided by both TAMs and EVT and will test expectancy, values, and costs as antecedents of both computer attitude and behavioral intentions.

```{r}
fitmod <- '

# factors

computer_attitudes =~ 
tam_computer_attitudes_6 +
tam_computer_attitudes_7 +
tam_computer_attitudes_8 +
tam_computer_attitudes_14
# tam_computer_attitudes_17

expectancy =~ 
expectancy_success__20 +
expectancy_success__21 +
expectancy_success__22 +
# expectancy_success__23 +
expectancy_success__24 +
expectancy_success__25

attainment =~ 
task_value_attainment_value_27 +
task_value_attainment_value_31 +
task_value_attainment_value_33 + 
task_value_attainment_value_36 +
task_value_attainment_value_38

interest =~
task_value_interest_value_29 + 
task_value_interest_value_32 +
task_value_interest_value_37 + 
task_value_interest_value_40

utility =~
task_value_utility_value_28 + 
task_value_utility_value_30 +
task_value_utility_value_34 + 
task_value_utility_value_35 +
task_value_utility_value_39

task_effort =~ 
full_cost_task_effort_cost_42 + 
full_cost_task_effort_cost_45 +
full_cost_task_effort_cost_46 + 
full_cost_task_effort_cost_51 +
full_cost_task_effort_cost_57

outside_effort =~
full_cost_outside_effort_cost_44 +
full_cost_outside_effort_cost_47 +
full_cost_outside_effort_cost_50 +
full_cost_outside_effort_cost_52

lova =~ 
full_cost_loss_valued_alternatives_43 +
full_cost_loss_valued_alternatives_49 +
full_cost_loss_valued_alternatives_53 + 
full_cost_loss_valued_alternatives_56

emotional_costs =~
full_cost_emotional_cost_41 + 
full_cost_emotional_cost_48 +
full_cost_emotional_cost_54 + 
full_cost_emotional_cost_55 +
full_cost_emotional_cost_58 + 
full_cost_emotional_cost_59

behavioral_intentions =~
intention_use__18 +
intention_use__19

# regressions 

computer_attitudes ~ expectancy
computer_attitudes ~ attainment
computer_attitudes ~ interest
computer_attitudes ~ utility
computer_attitudes ~ task_effort
computer_attitudes ~ outside_effort
computer_attitudes ~ lova
computer_attitudes ~ emotional_costs

behavioral_intentions ~ expectancy
behavioral_intentions ~ attainment
behavioral_intentions ~ interest
behavioral_intentions ~ utility
behavioral_intentions ~ task_effort
behavioral_intentions ~ outside_effort
behavioral_intentions ~ lova
behavioral_intentions ~ emotional_costs
behavioral_intentions ~ computer_attitudes
'

m2_4 <- sem(fitmod, data = d)
summary(m2_4, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
```

# Supplementary 

CFA 

```{r}

```

## Adding composites for 
```{r}
fitmod <- '

# factors 

computer_attitudes =~ 
tam_computer_attitudes_6 +
tam_computer_attitudes_7 +
tam_computer_attitudes_8 +
tam_computer_attitudes_14
# tam_computer_attitudes_17

expectancy =~ 
expectancy_success__20 +
expectancy_success__21 +
expectancy_success__22 +
# expectancy_success__23 +
expectancy_success__24 +
expectancy_success__25

attainment =~ 
task_value_attainment_value_27 +
task_value_attainment_value_31 +
task_value_attainment_value_33 + 
task_value_attainment_value_36 +
task_value_attainment_value_38

interest =~
task_value_interest_value_29 + 
task_value_interest_value_32 +
task_value_interest_value_37 + 
task_value_interest_value_40

utility =~
task_value_utility_value_28 + 
task_value_utility_value_30 +
task_value_utility_value_34 + 
task_value_utility_value_35 +
task_value_utility_value_39

task_effort =~ 
full_cost_task_effort_cost_42 + 
full_cost_task_effort_cost_45 +
full_cost_task_effort_cost_46 + 
full_cost_task_effort_cost_51 +
full_cost_task_effort_cost_57

outside_effort =~
full_cost_outside_effort_cost_44 +
full_cost_outside_effort_cost_47 +
full_cost_outside_effort_cost_50 +
full_cost_outside_effort_cost_52

lova =~ 
full_cost_loss_valued_alternatives_43 +
full_cost_loss_valued_alternatives_49 +
full_cost_loss_valued_alternatives_53 + 
full_cost_loss_valued_alternatives_56

emotional_costs =~
full_cost_emotional_cost_41 + 
full_cost_emotional_cost_48 +
full_cost_emotional_cost_54 + 
full_cost_emotional_cost_55 +
full_cost_emotional_cost_58 + 
full_cost_emotional_cost_59

behavioral_intentions =~
intention_use__18 +
intention_use__19

# regressions

expectancy ~ computer_attitudes
attainment ~ computer_attitudes
interest ~ computer_attitudes
utility ~ computer_attitudes
task_effort ~ computer_attitudes
outside_effort ~ computer_attitudes
lova ~ computer_attitudes
emotional_costs ~ computer_attitudes

behavioral_intentions ~ 
expectancy +
attainment +
interest +
utility +
task_effort +
outside_effort +
lova + 
emotional_costs
'

m4_1 <- sem(fitmod, data = d)
summary(m4_1, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
```